---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

spreadsheet <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS-Yd1nwbWs3rFJVIluP5nIta3cFbIkUF0WE8MhHB-gp64qeqWgR2up_DnUW9cl0Hq1FGRKyEmScpp1/pub?output=csv"

# Importing the data from the CSV
logged_data <- read_csv(spreadsheet)

# Renaming variables to clean uo
latest_data <- rename(logged_data,
                      muscle_group = 2,
                      body_mass = 3,
                      weight = 4,
                      sets = 5,
                      reps = 6)


# ============================================================================
# Commented Section for code to create summary values and Bar Charts
# ============================================================================

# Summary Values
mean_reps <- mean(latest_data$reps)
mean_sets <- mean(latest_data$sets)
max_weight <- max(latest_data$weight)
min_weight <- min(latest_data$weight)

# ============================================================================

# Calculate Intensity
intensity <- latest_data %>%
  
  # Group this by body type
  group_by(body_mass) %>%
  
  # Calculate average weight lifted for each body type
  summarise(avg_weight = mean(weight), .groups = "drop") %>%
  
  # Create Bar Plot
  ggplot(aes(x = body_mass, y = avg_weight, fill = body_mass)) +
  
  # Draw the bars
  geom_col() +
  
  # Add plot labels
  labs(
    title = "Average Intensity by Body Type",
    subtitle = "Measured by average weight lifted (kg)",
    x = "Body Type",
    y = "Average Weight (kg)",
    caption = "This shows how intensely each build tends to train"
  )

# ============================================================================

# Calculate average reps per body type
reps_plot <- latest_data %>%
  
  # Group by body type
  group_by(body_mass) %>%
  
  # Average reps
  summarise(avg_reps = mean(reps), .groups = "drop") %>%
  
  # Plot
  ggplot(aes(x = body_mass, y = avg_reps, fill = body_mass)) +
  geom_col() +
  labs(
    title = "Average Reps per Set by Body Type",
    subtitle = "How many reps each build performs per set",
    x = "Body Type",
    y = "Average Reps",
    caption = "This reflects training focus (endurance vs strength)"
  ) 

# ============================================================================

# Calculate average sets per body type
sets_plot <- latest_data %>%
  
  # Group by body type
  group_by(body_mass) %>%
  
  # Average sets
  summarise(avg_sets = mean(sets), .groups = "drop") %>%
  
  # Plot
  ggplot(aes(x = body_mass, y = avg_sets, fill = body_mass)) +
  geom_col() +
  labs(
    title = "Average Sets per Session by Body Type",
    subtitle = "How many sets each build performs",
    x = "Body Type",
    y = "Average Sets",
    caption = "This shows how much each build focuses on volume or session length"
  ) 
```

```{css}
/*CSS CODE BLOCK FOR MARKDOWN FILE*/

/* initialising variables to later reference in css styling */
:root {
    --text-color: #1a1c20;
    --link-color: #4a76ee;
    --background-color: #f5f5f7;
    --header-bg: #ffffff;
    --box-shadow: rgba(0, 0, 0, 0.1);
    --border-radius: 8px;
}

/* main body of html */
body {
    font-family: 'Poppins', sans-serif;
    color: var(--text-color);
    background-color: var(--background-color);
    max-width: 1000px;
    margin: 20px auto;
    padding: 20px;
    line-height: 1.6;
}

p {
    background-color: white;  /* Set background to white */
    padding: 10px;
    border-radius: 8px; 
    box-shadow: 0px 2px 4px rgba(0, 0, 0, 0.1);
}

/* all levels of headers */
h1, h2, h3 {
    color: var(--text-color);
    margin-bottom: 10px;
    font-weight: bold;
}

/* individual adjustments to header*/
h1 {
    font-size: 36px;
    font-weight: 700;
}

h2 {
    font-size: 28px;
    border-bottom: 2px solid var(--text-color);
    padding-bottom: 5px;
}

/* link to my github */
a {
    color: var(--link-color);
    text-decoration: none;
    font-weight: 600;
}

/* mouse hovering over the link */
a:hover {
    text-decoration: underline;
}

/* Images */
img {
    display: block;
    max-width: 100%;
    height: auto;
    margin: 10px auto;
    border-radius: var(--border-radius);
    box-shadow: 0px 4px 8px var(--box-shadow);
}

/* coding blocks */
pre {
    background-color: #2d2d2d;
    color: #f8f8f2;
    padding: 15px;
    border-radius: var(--border-radius);
    overflow-x: auto;
}

code {
    font-family: 'Courier New', monospace;
    background: #eeeeee;
    padding: 3px 6px;
    border-radius: 4px;
}
```
## How different body types train

This report in seeing in how the different body types differ in...

- Weight lifted
- Reps per set
- Sets per session

We look into how each body type approaches their training, whether their prioritise lifiting heavy, doing more sets, or performing more reps.

## Average Weight Lifted
```{r}
intensity
```

- The lightest weight lifted: `r min_weight` 
- The heaviest weight lifted: `r max_weight`

## Average Reps per Set

``` {r}
reps_plot
```

Averaging around `r signif(mean_reps,2)` reps across all groups.

## Average Sets per Session

``` {r}
sets_plot
```

They seem to not have that much of a difference, everyone tends to train around `r signif(mean_sets,2)` sets.
